---
title: "Untitled"
format: html
---

# Notebook: Analysis of openFDA Data

## Section 1: Setup and Data Acquisition

```{r}
# Comment: Import necessary R packages such as tidyverse, ggplot2, dplyr, and openfda.
# Prompt Copilot to provide the code for importing these libraries.


```



```{r}
# Comment: Define a function to fetch data from openFDA API.
# Prompt Copilot for creating a function that takes parameters like endpoint, query
# Make sure to handle exceptions and errors in the API call.




```






```{r}
# Comment: Choose a dataset from openFDA to analyze, such as drug adverse events or food recalls. Limit for top 3 events.
# Discuss why you chose this dataset.

# Example: Analyzing drug adverse events dataset

```


## Section 2: Data Loading and Preprocessing


```{r}
# Comment: Load the data into a r DataFrame.
# Prompt Copilot to write code for converting JSON API response into a r DataFrame.




```


# Comment: Clean and preprocess the data.
# Discuss common data cleaning steps like handling missing values, filtering columns, and type conversion.
# Prompt Copilot to implement these.
```{r}

```


## Section 3: Exploratory Data Analysis (EDA)

# Comment: Perform basic EDA including summary statistics and distribution of key variables.
# Prompt Copilot to use pandas and matplotlib/seaborn for these tasks.
```{r}

```


# Comment: Identify any outliers or anomalies in the data.
# Discuss methods to detect these, like IQR or Z-score, and prompt Copilot to implement.
```{r}

```


# Comment: Generate visualizations to understand relationships between variables.
# Examples include correlation heatmaps, scatter plots, and histograms. Prompt Copilot for code.
```{r}

```


## Section 4: Deeper Analysis

# Comment: Focus on a specific aspect of the dataset, like time trends in drug adverse events.
# Discuss what insights might be interesting and prompt Copilot for appropriate time series analysis.
```{r}

```


# Comment: Analyze the geographical distribution of data if location information is available.
# Discuss plotting data on maps using libraries like folium or plotly.
```{r}

```


# Comment: Use statistical tests to analyze differences or trends in the data.
# Examples include t-tests, chi-square tests, or ANOVA. Prompt Copilot to explain and implement these tests.
```{r}

```


## Section 5: Conclusions and Further Research

# Comment: Summarize the key findings from the analysis.
# Discuss any limitations of the analysis and the data.
```{r}

```


# Comment: Suggest further areas of research or additional data that could be integrated.
# Discuss potential machine learning models or predictive analytics that could be applied.
```{r}

```


# Comment: Discuss ethical considerations in data analysis, particularly with medical data.
# Prompt Copilot to provide insights on handling sensitive data responsibly.
```{r}

```


## Section 6: Exporting Results

# Comment: Save the cleaned data, figures, and statistical test results to files.
# Prompt Copilot to provide code for exporting data to CSV, images to PNG, and results to a text file.
```{r}

```


# Comment: Provide instructions on how to interpret the exported files and data.
# Discuss best practices for documentation and reproducibility.
```{r}

```

